%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {.NET Developer} % Job title
    {Stretto Sp. z o.o.} % Organization
    {Łódź, Poland} % Location
    {Dec. 2021 - Mar. 2026} % Date(s)
    {
      \begin{cvitems} % Description
        \item {\textbf{Modernized Legacy Infrastructure}: Led the migration of high-risk legacy modules to modern \textbf{.NET architectures}, pioneering the company’s first \textbf{Dockerized} container deployments to significantly improve system stability and long-term maintainability.}
        \item {\textbf{Architected Serverless Solutions}: Designed and deployed \textbf{.NET Web APIs using AWS Lambda}, leveraging cloud scalability to reduce infrastructure overhead costs while ensuring 24/7 high availability for global clients.}
        \item {\textbf{Delivered High-Adoption Data Tools}: Engineered a high-performance \textbf{ASP.NET tool} for automated CSV-to-DB synchronization that earned \textbf{critical acclaim} from clients and internal teams, serving as a key competitive differentiator and driving client retention.}
        \item {\textbf{Strengthened Security \& Compliance}: Hardened application security by implementing \textbf{AWS Cognito (MFA)} and Google reCaptcha, playing a pivotal role in achieving and maintaining \textbf{SOC Compliance} for sensitive financial data.}
        \item {\textbf{Automated Financial Workflows}: Streamlined corporate restructuring and bank statement generation by developing automated transaction deserialization tools, eliminating manual document handling and increasing team operational capacity.}
        \item {\textbf{Optimized SDLC \& Code Quality}: Integrated \textbf{SonarQube} and \textbf{Dependency Track} into the development lifecycle to proactively mitigate vulnerabilities, while configuring \textbf{Bamboo CI/CD pipelines} to accelerate the release of secure, stable software.}
        \item {\textbf{International Collaboration}: Partnered with US-based Product Owners and QA teams within an Agile framework to deliver complex features, including the full-scale integration of a new banking partner that directly increased company revenue.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {.NET Developer} % Job title
    {E-surf Software Sp. z o.o.} % Organization
    {Poznań, Poland} % Location
    {Jun. 2020 - Nov. 2021} % Date(s)
    {
      \begin{cvitems} % Description
        \item {\textbf{Engineered and maintained a mission-critical, multithreaded WPF application (Alvo Integra)} used in operating rooms, optimizing UI responsiveness and hardware control for medical staff during surgical procedures.}
        \item {\textbf{Architected and implemented scalable .NET Core microservices} to facilitate seamless communication between software layers and medical hardware, ensuring high system availability in high-stakes environments.}
        \item {\textbf{Developed low-latency, real-time communication systems} using \textbf{SignalR} and \textbf{Modbus TCP} protocols, enabling instantaneous synchronization and control of surgical lamps, cameras, and operating tables.}
        \item {\textbf{Designed and optimized database schemas} using \textbf{Microsoft SQL Server}, ensuring high-performance data persistence for surgical logs, video recordings, and device configurations.}
        \item {\textbf{Improved software reliability and code quality} by authoring comprehensive \textbf{Unit Tests} for core modules, significantly reducing post-deployment bugs and accelerating the release cycle.}
        \item {\textbf{Leveraged Microsoft Azure DevOps} within an \textbf{Agile/Scrum} framework to streamline CI/CD pipelines and sprint delivery, resulting in faster feature deployment and more transparent project tracking.}
        \item {\textbf{Bridged the gap between technical requirements and clinical needs} by conducting on-site hardware integration testing at medical facilities, ensuring that software solutions met the rigorous demands of healthcare environments.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {.NET Developer} % Job title
    {eXant sp. z o.o.} % Organization
    {Poznań, Poland} % Location
    {Sep. 2019 - May 2020} % Date(s)
    {
      \begin{cvitems} % Description
        \item {\textbf{Developed and scaled} a comprehensive project management platform for a real estate developer using \textbf{ASP.NET} and \textbf{AngularJS}, streamlining task management and cross-team communication.}
        \item {\textbf{Architected and optimized} relational databases in \textbf{Microsoft SQL Server}, ensuring high data integrity and performance for complex project-tracking and financial modules.}
        \item {\textbf{Collaborated directly with the Project Owner} to refine business requirements and translate them into technical features, ensuring the final product met specific stakeholder needs.}
        \item {\textbf{Delivered responsive user interfaces} by integrating \textbf{AngularJS} with \textbf{ASP.NET} backends, improving the end-user experience and the overall usability of the management system.}
        \item {\textbf{Championed code quality} through the implementation of \textbf{unit tests} for core system modules, reducing regression issues and increasing long-term maintainability.}
        \item {\textbf{Facilitated rapid feature delivery} using \textbf{Kanban} methodology and \textbf{Team Foundation Server (TFS)}, optimizing the development lifecycle and version control processes.}
        \item {\textbf{Drove business growth} by accelerating the deployment of new features, which directly led to increased client satisfaction and improved financial performance for the client.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {.NET Developer} % Job title
    {eFitness sp. z o.o.} % Organization
    {Poznań, Poland} % Location
    {Sep. 2017 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description
        \item {\textbf{Architected System Modernization:} Developed Proof of Concepts (PoCs) and conducted rigorous framework evaluations to drive the architectural direction for the Alvo Integra system rewrite, enabling informed stakeholder decision-making.}
        \item {\textbf{Engineered Full-Stack Gym Solutions:} Developed and scaled core modules for client management and reservations using \textbf{ASP.NET Razor}, \textbf{JavaScript}, and \textbf{MS SQL Server}, optimizing team workflows and cross-departmental communication.}
        \item {\textbf{High-Performance Data Engineering:} Designed and implemented a custom data migration application to facilitate seamless transfers between systems while managing \textbf{Big Data} environments and complex SQL structures.}
        \item {\textbf{Hardware \& IoT Integration:} Developed automated access control systems for gym entry gates and integrated fiscal printer protocols, expanding system functionality and improving the physical user experience.}
        \item {\textbf{Refactoring \& Technical Debt Reduction:} Systematically refactored legacy modules to improve code readability and maintainability, significantly reducing the long-term cost of feature development and bug fixing.}
        \item {\textbf{Quality Assurance \& Unit Testing:} Established higher software reliability by implementing comprehensive \textbf{unit testing} suites, ensuring the stability of critical modules and accelerating the identification of regression bugs.}
        \item {\textbf{Agile DevOps Excellence:} Optimized the software delivery lifecycle using \textbf{Microsoft Azure DevOps} within a \textbf{Scrum} framework, maintaining high velocity and rapid response times to client-reported issues even with incomplete documentation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {.NET Developer} % Job title
    {ARP Ideas sp. z o.o.} % Organization
    {Poznań, Poland} % Location
    {Feb. 2016 - Jul. 2017} % Date(s)
    {
      \begin{cvitems} % Description
        \item {\textbf{Engineered custom Dynamics CRM plugins and workflows} using \textbf{C\#} to automate complex business logic, significantly reducing manual data entry for enterprise clients.}
        \item{\textbf{Developed and deployed serverless Azure Functions} to handle high-volume background processing and asynchronous tasks, optimizing cloud infrastructure costs and system scalability.}
        \item{\textbf{Architected a comprehensive sales management system} for a real estate development firm, leveraging \textbf{.NET} and \textbf{Dynamics CRM} to streamline the lead-to-contract pipeline.}
        \item{\textbf{Designed and implemented a warehouse management solution} for a large-scale footwear retailer, focusing on real-time inventory tracking and integration with \textbf{Microsoft SQL Server}.}
        \item{\textbf{Enhanced software maintainability and reliability} by authoring comprehensive \textbf{unit tests} for CRM plugins, ensuring code stability during complex version upgrades.}
        \item{\textbf{Optimized Microsoft SQL Server database performance} by designing efficient schemas and stored procedures, improving data retrieval speeds for high-traffic sales modules.}
        \item{\textbf{Collaborated within an Agile (Scrum) framework} using \textbf{TFS (Git)} for version control and CI/CD, consistently delivering high-quality code through rigorous peer reviews and sprint planning.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
